---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "##",
  fig.path  = "README_files/figures",
  out.width = "100%"
)
```


# omdbr

<!-- badges: start -->
<!-- badges: end -->

The package `omdbr` is an R client to the [OMDb API](http://www.omdbapi.com).
User can retrieve informations about a given movie (title, actors, year, genres, etc.)
and download movie poster (if available).

<br />

## Installation

To install the `omdbr` package:

```{r echo = TRUE, eval = FALSE}
remotes::install_github("inSileco/omdbr")
library(omdbr)
```

<br />

## Prerequisites

This package uses the [OMDb API](http://www.omdbapi.com) to access data on movies.
You have to obtained an API key [here](http://www.omdbapi.com/apikey.aspx).
When using the package for the first time, you'll be guided to store your API key.

<br />

## Usage

Let's get informations and cover about the
[The Darjeeling Limited](https://imdb.com/title/tt0838221) movie directed by
[Wes Anderson](https://en.wikipedia.org/wiki/Wes_Anderson). For the moment, the
package requires the IMDb Identifier of the movie. You can find this ID by
searching the movie on the [IMDb website](https://imdb.com) and extract it from
the URL (format: tt9999999).

The URL of _The Darjeeling Limited_ is:
[https://imdb.com/title/tt0838221](https://imdb.com/title/tt0838221), and the
IMDb ID is: `tt0838221`.

```{r echo = TRUE, eval = TRUE}
imdb_id <- "tt0838221"             ## imdb id of the movie
path    <- "~/Desktop/medias"      ## folder to store results
```

<br />

Let's retrieve informations about the movie with the function `get_details()`:

```{r echo = TRUE, eval = TRUE}
## Get informations about the movie ----
x <- get_details(imdb_id, path)
```

<br />

Now, we can try to download the movie poster with the function `get_cover()`:

```{r echo = TRUE, eval = TRUE}
## Download movie poster ----
get_cover(imdb_id, path)
```


<br />

What about
[The Grand Budapest Hotel](https://imdb.com/title/tt2278388),
[The Life Aquatic with Steve Zissou](https://imdb.com/title/tt0362270), and
[Moonrise Kingdom](https://www.imdb.com/title/tt1748122)?


```{r echo = FALSE, eval = TRUE}
imdb_ids <- c("tt2278388", "tt0362270", "tt1748122")
for (imdb_id in imdb_ids) {
  x <- get_details(imdb_id, path)
  get_cover(imdb_id, path)
  cat("\n")
}
```

<br />

<p align="center">
```{r cover2, echo = FALSE, eval = TRUE, out.width = "24.5%", out.extra='style="background-color: white; padding:2px; display: inline-block;"'}
tdl <- "README_files/figures/tt0838221.jpg"
knitr::include_graphics(tdl)
tdl <- "README_files/figures/tt2278388.jpg"
knitr::include_graphics(tdl)
tdl <- "README_files/figures/tt0362270.jpg"
knitr::include_graphics(tdl)
tdl <- "README_files/figures/tt1748122.jpg"
knitr::include_graphics(tdl)
```
</p>

<br />


Results are stored as follow:

```{r echo = TRUE, eval = FALSE}
├── covers
│   ├── tt0362270.jpg
│   ├── tt0838221.jpg
│   ├── tt1748122.jpg
│   └── tt2278388.jpg
└── data
    ├── tt0362270.yml
    ├── tt0838221.yml
    ├── tt1748122.yml
    └── tt2278388.yml

2 directories, 8 files
```

<br />


## Coming soon

- [ ] Implement `find_imdb_id()` function to search for terms
